Medical Concept Extraction

### 2012-12-14 paper/paper.tex
intro paragraph to stemming

\subsubsection{Porter Stemmer}
Our CRF F1 scores went from 0.58 to 0.82

@@

\subsubsection{Snowball Stemmer}

>>>>

\subsubsection{Porter Stemmer}
We already discussed the benefits of using entire words as features, but similar words come in many different forms. Motivated by generalization, we chose to use word stems as features and approached this feature extraction using three different stemming algorithms--two at the word-level and one at the sentence level (See 5.3.2). Namely, we used the Porter Stemming Algorithm, as developed by Martin Porter.

Our CRF F1 scores went from 0.58 to 0.82

@@
